Weekday sleep, total cholestrol and the modifying effect of age on systolic blood pressure: An analysis of the 2015-2018 non-obese NHANES population

### 2023-12-11 manuscript/paper.Rmd

Table \@ref(tab:tabmodel) summarizes the performance metrics across the
different models fitted to the data in our investigation.

@@

\caption{\label{tab:tabmodel}Summary model performance measures.}
\centering
\begin{tabular}[t]{lrrrrrr}
\toprule
  & df & AIC & BIC & MSE & $R^2$ & Adjusted $R^2$\\
\midrule
Model 1 & 44 & 15888.48 & 16134.41 & 173.17 & 0.36 & 0.34\\
Model 2 & 45 & 15849.26 & 16100.78 & 169.60 & 0.37 & 0.36\\
Model 3 & 39 & 15883.76 & 16101.74 & 173.63 & 0.36 & 0.34\\
Model 4 & 600 & 16156.48 & 19510.09 & 113.00 & 0.58 & 0.40\\
Model 5 & 40 & 15848.93 & 16072.50 & 170.43 & 0.37 & 0.35\\
\addlinespace
Model 6 & 41 & 15888.38 & 16117.55 & 173.69 & 0.36 & 0.34\\
Model 7 & 25 & 15877.41 & 16017.15 & 2657.01 & 0.35 & 0.34\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{a} df = degrees of freedom}\\
\multicolumn{7}{l}{\textsuperscript{b} AIC = Akaike Information Criteria}\\
\multicolumn{7}{l}{\textsuperscript{c} BIC = Bayesian Information Criteria}\\
\multicolumn{7}{l}{\textsuperscript{d} MSE = Mean Squared Error}\\
\end{tabular}
\end{table}
```

@@

In response to this challenge, we propose the implementation of multiple
imputation techniques. This approach involves generating multiple
plausible sets of missing values based on observed data patterns. By
imputing missing values using this method, we aim to enhance the
completeness of our dataset. This strategy is intended to mitigate
potential biases resulting from missing data and fortify the reliability
and accuracy of our analytical outcomes.

# Refences

>>>>

Table \@ref(tab:tabmodel) presents an overview of the performance measures of the various models applied
to our data set. Model 6, utilizing best subset selection, revealed
notably high MSE, suggesting limited predictive efficacy. Models 1 and
2, not including variable selection techniques, highlight the impact of
incorporating the age-cholesterol interaction term with notable reduction
in MSE. Models 3, 4, and 5 included solely significant univariate
regression variables. Model 5, with the lowest AIC and second lowest
BIC, demonstrates an acceptable MSE. Model 4, with the lowest MSE and
highest \$R\^2\$, demonstrated a high predictive power, although its extensive number of terms
raise concerns of potential overfitting. Model 3, based solely on
significant univariate covariates, performed well but exhibited a higher
MSE than Models 4 and 5, suggesting the probable influence of
interaction terms. Models 7 and 8, employing LASSO, exhibited comparable
performance metrics, with Model 8 displaying reduced BIC and MSE,
attributed chiefly to the significant inclusion of an age-cholesterol
interaction term.

@@

\caption{\label{tab:tabmodel}Summary model performance measures.}
\centering
\begin{tabular}[t]{lrrrrrr}
\toprule
  & $\text{df}^a$ & $\text{AIC}^b$ & $\text{BIC}^c$ & $\text{MSE}^d$ & $R^2$ & Adjusted $R^2$\\
\midrule
Model 1 & 44 & 15888.48 & 16134.41 & 173.17 & 0.36 & 0.34\\
Model 2 & 45 & 15849.26 & 16100.78 & 169.60 & 0.37 & 0.36\\
Model 3 & 39 & 15883.76 & 16101.74 & 173.63 & 0.36 & 0.34\\
Model 4 & 600 & 16156.48 & 19510.09 & 113.00 & 0.58 & 0.40\\
Model 5 & 40 & 15848.93 & 16072.50 & 170.43 & 0.37 & 0.35\\
\addlinespace
Model 6 & 25 & 15877.41 & 16017.15 & 2657.01 & 0.35 & 0.34\\
Model 7 & 41 & 15888.38 & 16117.55 & 173.69  & 0.36 & 0.34\\
Model 8 & 42 & 15849.19 & 16083.94 & 170.11  & 0.37 & 0.36\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{a} df = degrees of freedom}\\
\multicolumn{7}{l}{\textsuperscript{b} AIC = Akaike Information Criteria}\\
\multicolumn{7}{l}{\textsuperscript{c} BIC = Bayesian Information Criteria}\\
\multicolumn{7}{l}{\textsuperscript{d} MSE = Mean Squared Error}\\
\end{tabular}
\end{table}
```

@@

In response to this challenge, we propose the implementation of multiple
imputation techniques. This approach involves generating multiple
plausible sets of missing values based on observed data patterns. By
imputing missing values using this method, we aim to enhance the
completeness of our data set. This strategy is intended to mitigate
potential biases resulting from missing data and fortify the reliability
and accuracy of our analytical outcomes.

# References
